---
title: "covid 19"
author: "Adesuwa Mukoro"
date: "10/20/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent

```{r}
barchartGC(~result + Sex,data=kRdata, main ="Frequency Bar Chart")
```

  
### this bar chart is displaying in total frequency terms our data.  Clearly there are a lot less dead people than alive people as is reflected by the sizes of the bars in the display.  

```{r}
barchartGC(~result + Sex,data=kRdata,type="percent",  main ="percent Bar Chart")
```

The percentage of females with the virus is more than the percentage of males, but the percentage of females dying is less than males. The percentage of males with the virus is less than females, but the percentage of males dying is more than females.

  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
The females alive is 56% and males alive is 44%. The females dead is 36% and males is 64%. Of all the females, 98% are still alive, but 1.4 percent of them are dead. Of all the males, 97% of them are still alive, but 3% of them are dead. The amount of males that are dead is about twice as great as the amount of dead people that are females.



## Inferential results 




## Conclusions

